The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-04 author.tex
replace empty affiliation with noaffiliation
Postal code University of Toronto
I seem to have initially added that of my home. SIgh...

\collaboration{Primary paper contributors:}

@@

\author[0000-0002-3713-6337]{B. M. Sip\H{o}cz}
\affiliation{}

@@

\collaboration{Astropy coordination committee:}

@@

\collaboration{Astropy contributors:}

@@

\author{A. V. Bakanov}
\affiliation{}

@@

\author{K. L. Berry}
\affiliation{}

@@

\author{E. M. Bray}
\affiliation{}

@@

\author[0000-0002-5317-7518]{Y. Copin}
\affiliation{CNRS/IN2P3, Institut de Physique Nucleaire de Lyon, Universite de Lyon, Universite de Lyon 1, Villeurbanne, F-69622, Lyon, France}

@@

@@

\author{T. Finethy}
\affiliation{}

\author[0000-0003-4291-1091]{R. T. Fox}
\affiliation{}

@@

\author{F. Grollier}
\affiliation{}

@@

\author{A. Khvalko}
\affiliation{}

@@

\author{R. Patil}
\affiliation{}

@@

\author{T. Rastogi}
\affiliation{}

@@

\author{M. Seifert}
\affiliation{}

@@

\author[0000-0003-0477-6220]{H. Sherwood-Taylor}
\affiliation{}

@@

\author{M. T. Silbiger}
\affiliation{}

@@

\author{K. A. Sooley}
\affiliation{}

\author{S. Sornarajah}
\affiliation{}

@@

\author[0000-0002-5830-8505]{M. H. van Kerkwijk}
\affiliation{Department of Astronomy \& Astrophysics, University of Toronto, 50 Saint George Street, Toronto, ON M5R 3B3, Canada}

@@

\author{J. Xavier Prochaska}
\affiliation{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}

\author[0000-0003-2638-7648]{V. Zabalza}
\affiliation{}

>>>>

@@

\author[0000-0002-3713-6337]{B. M. Sip\H{o}cz}
\noaffiliation

@@

\collaboration{(primary paper contributors)}

@@

\collaboration{(Astropy coordination committee)}

@@

\author{A. V. Bakanov}
\noaffiliation

@@

\author{K. L. Berry}
\noaffiliation

@@

\author{E. M. Bray}
\noaffiliation

@@

\author[0000-0002-5317-7518]{Y. Copin}
\affiliation{Universit\'e de Lyon, F-69622, Lyon, France; Universit\'e de Lyon 1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon}

@@

\author{M. Droettboom}
\affiliation{\afstsci}

@@

\author{T. Finethy}
\noaffiliation

\author[0000-0003-4291-1091]{R. T. Fox}
\noaffiliation

@@

\author{F. Grollier}
\noaffiliation

@@

\author{A. Khvalko}
\noaffiliation

@@

\author{R. Patil}
\noaffiliation

@@

\author{J. X. Prochaska}
\affiliation{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}

\author{T. Rastogi}
\noaffiliation

@@

\author{M. Seifert}
\noaffiliation

@@

\author[0000-0003-0477-6220]{H. Sherwood-Taylor}
\noaffiliation

@@

\author{M. T. Silbiger}
\noaffiliation

@@

\author{K. A. Sooley}
\noaffiliation

\author{S. Sornarajah}
\noaffiliation

@@

\author[0000-0002-5830-8505]{M. H. van Kerkwijk}
\affiliation{Department of Astronomy \& Astrophysics, University of Toronto, 50 Saint George Street, Toronto, ON M5S 3H4, Canada}

@@

\author[0000-0003-2638-7648]{V. Zabalza}
\noaffiliation

\collaboration{(Astropy contributors)}
